Application for Rethinking Foundations of Physics 2017

### 2017-01-13 Rethinking Foundations of Physics 2017/application.tex
application.tex \section{Proposed Question} Copied from general plan...

>>>>

A major aim of this proposal is to recast quantum probability and
measurement in a computational resource-aware setting. Our vision is
to unify the strands above in a novel way as explained in this
section. We start with some immediate observations that justify the
rest of the development.

\item If we insist that probabilities cannot be computed to infinite
  precision and are bound to be approximations represented by
  intervals of confidence, then quantum states themselves can only be
  discussed within intervals of confidence. This raises an important
  philosophical question with immense practical relevance in the
  context of quantum computing. The question, which we could largely
  bypass in the classical case, is whether there is, in the background
  of all the measurements and probabilities, a ``real''
  infinitely-precise quantum state that is being approximated and
  that, in principle, can be more and more accurately described given
  more and more resources. In other words, does a Gleason,
  Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
  or Kochen-Specker theorem still hold in a world with finite
  resources?  The answer will have to be \emph{no} if we are to
  respect these major theorems of quantum mechanics and quantum
  information. Thus our first radical departure from the conventional
  case will be that the quantum state itself must be fuzzy in some
  sense to be formalized.

\item Going further we actually have to concede not just the infinite
  accuracy of the quantum state, but its very existence as a ``real''
  entity that exists independently of measurements and
  probabilities. The reasons for this second radical position are as
  follows. First arguments embedded in the proof of the Kochen-Specker
  theorem essentially rule out the existence of a sample space as the
  probabilities of events cannot be consistently expressed using core
  assignments to elements of the sample space. Second, the frequency
  interpretation of probability which is already problematic in the
  classical case, becomes untenable in the quantum case. In both
  cases, but much more in the quantum case, it is much more sensible
  to interpret probability in the Bayesian sense as ``lack of
  knowledge''. This, and similar arguments elegantly expressed by
  recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
  suggest that the quantum state is more like an interactive system in
  computer science parlance. In other words, the state is only
  determined by its interactions with the environment or observers. A
  rough but useful analogy in the context of computer science would be
  a web server: the state of such a system cannot be said to exist
  independently of the interactions with clients; each interaction
  with a client determines a future state of the system and may affect
  future interactions. Crucially, each client may have a
  \emph{different} view of the web server that is consistent with
  their own history of interactions. This computational perspective
  agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
  that asserts that the quantum state is subjective: each observer has
  a different view of the quantum system that is consistent with their
  previous observations and that allows that observer, independently
  of other observers, to assign beliefs (i.e., probabilities) to
  possible future interactions.
